---
title: "CellOmicsR-Tutorial"
author: "Jinlian Li"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    # theme: cayman # 1
    # theme: tactile #2
    # theme: architect #3
    # theme: leonids #4
    theme: hpstr #5
    highlight: github
    # highlight: vignette
---

```{r setup, include = T, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`CellOmicsR` is designed for bioinformatics research and analysis. 

## Vignette Info

This vignette shows how to use CellOmicsR function.

```{r, include=TRUE, eval=FALSE}
install.packages("devtools")
devtools::install_github("L7991-lian/CellOmicsR")

```


## Plot Graph Network

Please note that the shape of the graph may change every time you run, so you can try multiple times to achieve the desired visualization effect.

### (1)input data
```{r}
# 
library(igraph)
dataframe <- data.frame(
  source = c("A", "A", "B", "B", "C", "C", "B", "C", "D", "E", "F", "D", "D", "F"),
  target = c("B", "C", "D", "C", "E", "B", "A", "F", "A", "D", "E", "F", "B", "A"),
  value = c(5, 10, 0.9, 9, 7, 6, 1, 3, 8, 3, 8, 14, 2, 5)
)

head(dataframe)
```

### (2) network graph
```{r}
colors <- c(A = "#EE4000", B = "#0000CD", C = "#66CC00", D = rgb(102/255,46/255,115/255), E = rgb(31/255,153/255,139/255), F = "#003366")

CellOmicsR::plot_graph_network(dataframe, sendercolumn = "source", receivercolumn = "target", widthcolumn = "value", useLabels = T, threshold = 0.01, colors = colors, nodeSize = 10, vertex.label.color = "white", edge.label.color = "black", edge.label.cex = 1.2) 

```


## plot stacked bar

### (1)input data
```{r}
library(CellOmicsR, verbose = F)
```

```{r}
# input data: a data.frame 
cell_data <- data.frame( Sample = rep(c("Sample1", "Sample2", "Sample3"), each = 4),Type = rep(c("Type1", "Type2", "Type3", "Type4"), 3),Count = c(10, 15, 8, 6, 5, 7, 12, 9, 3, 6, 4, 11))

head(cell_data)
```

### (2) bar plot
```{r, eval=TRUE}
bar_p <- CellOmicsR::plot_stacked_bar(data = cell_data, x_col = Sample, stack_col = Count, fill_col = Type)

bar_p
```


footnotes^[plot_stacked_bar will return a bar plot]

([via](https://github.com/L7991-lian))

***END!***
